The \project{unRAVE} catalog

### 2016-09-05 article/unrave.tex
Remove color box for Traivs
common color scheme for log density; bug fix in figure ref
Update regularization figure

\usepackage{amsmath}
\usepackage{bm}
\usepackage{xcolor}

\definecolor{unoffensive-warning}{HTML}{B4DCED}

% This section can be removed at submission.
% ------------------------------------------
%\usepackage{color}
\usepackage{datenumber}

@@

% TODO: Replace ZENODO-URL with a data url
\noindent\colorbox{unoffensive-warning}{\parbox{\dimexpr\linewidth-2\fboxsep}{
\noindent{}Source code for this project is available at \texttt{\giturl}\hspace{-0.5em},
and this document was compiled from revision hash \texttt{\githash} in that repository.
Inferred labels, covariance matrices, and relevant metadata are available electronically
at \texttt{\url{ZENODO-URL}} \citep{DATA_REPOSITORY}.  Please note that it is a condition
of using these results that the fifth \rave\ data release by \citet{Kunder_2016} must 
also be cited, as the work presented here would not have been possible without the 
tireless efforts of the entire \rave\ collaboration, past and present.
}}

@@

\begin{figure}[p]
\includegraphics[width=\textwidth]{figures/set-giant-regularization.pdf}
\caption{The fractional improvement in RMS deviation between inferred and training labels for the 9-label giant model at different regularization strengths.  The RMS values were calculated by leave-one-out cross-validation.  The points and solid line indicate the mean improvement across all labels. The filled area represents the minimum and maximum improvements across all labels.  The maximum improvement (decrease) in RMS label deviations occurs at $\Lambda \approx 0.3$, and this improvement persists until $\Lambda \approx 0.6$.\label{fig:set-hyperparameters}}
\end{figure}

@@

\begin{figure*}[p]
\includegraphics[width=\textwidth]{figures/dr4-comparison.png}
\caption{Stellar label comparison between the \project{UNRAVE} catalog and the \project{RAVE} fourth data release \citep{Kordopatis_2013}.\label{fig:rave-dr4-comparison}}
\end{figure*}

>>>>

\usepackage{amsmath}
\usepackage{bm}

%\usepackage{xcolor}
%\definecolor{unoffensive-warning}{HTML}{B4DCED}

% This section can be removed at submission.
% ------------------------------------------
\usepackage{color}
\usepackage{datenumber}

@@

% TODO: Replace ZENODO-URL with a data url
%\noindent\colorbox{unoffensive-warning}{\parbox{\dimexpr\linewidth-2\fboxsep}{
\noindent{}Source code for this project is available at \texttt{\giturl}\hspace{-0.5em},
and this document was compiled from revision hash \texttt{\githash} in that repository.
Inferred labels, covariance matrices, and relevant metadata are available electronically
at \texttt{\url{ZENODO-URL}} \citep{DATA_REPOSITORY}.  Please note that it is a condition
of using these results that the fifth \rave\ data release by \citet{Kunder_2016} must 
also be cited, as the work presented here would not have been possible without the 
tireless efforts of the entire \rave\ collaboration, past and present.
%}}

@@

\begin{figure}[p]
\includegraphics[width=\textwidth]{figures/set-hyperparameters.pdf}
\caption{The percentage change in RMS deviation between inferred and training labels at different regularization strengths.  The RMS values were calculated by leave-one-out cross-validation.  The points and solid line indicate the mean improvement across all labels. The filled area represents the minimum and maximum improvements across all labels.\label{fig:set-hyperparameters}}
\end{figure}

@@

\begin{figure*}[p]
\includegraphics[width=\textwidth]{figures/dr4-comparison.pdf}
\caption{Stellar label comparison between the \project{UNRAVE} catalog and the \project{RAVE} fourth data release \citep{Kordopatis_2013}.\label{fig:rave-dr4-comparison}}
\end{figure*}
